A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases. The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model. Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b). When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable. For example:
\begin{enumerate}
\item The model retains heterogeneity within each region
\item A single realization will be obtained for the same upgrid resolution
  \item The correlation to local heterogeniety in the base case is maintained
\end{enumerate}

Figure~\ref{fig:Saturationfield4_3DCases}(a)-(c) and Figure~\ref{fig:Saturationfield4_3DCases}(d)-(f) show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,

\begin{displaymath}
  t = 0.18,~0.28\text{ and } 0.42 \text{ s.} 
\end{displaymath}

Figure~\ref{fig:Saturationfield4_3DCases}(a) and (d), which represent the phase 1 saturation distribution for the base case and the 3-D PCA-LinReg case respectively at time $t = 0.18$, retain the mesh grid to give a more details view of the flow pattern. Comparing, Figure~\ref{fig:Saturationfield4_3DCases}(b) and (e) as well as Figure~\ref{fig:Saturationfield4_3DCases}(c) and (f) indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern. A detailed quantitative analysis of this upscaled model will be presented in the authors' future work.

>>>>

Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases. The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model. Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b). When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable. For example:
\begin{enumerate}
  \item The model retains heterogeneity within each region;
  \item A single realization will be obtained for the same upgrid resolution;
  \item The correlation to local heterogeniety in the BaseCase is maintained.
\end{enumerate}

Figures~\ref{fig:Saturationfield4_3DCases}a-c and Figs.~\ref{fig:Saturationfield4_3DCases}d-f show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
\begin{displaymath}
  t = 0.18,~0.28\text{ and } 0.42 \text{ s.} 
\end{displaymath}

Figures~\ref{fig:Saturationfield4_3DCases}a,d, which represent the phase 1 saturation distribution for the BaseCase and the 3-D PCA-LinReg case, respectively at time $t = 0.18$, retain the mesh grid to give more details view of the flow pattern. Comparing Figs.~\ref{fig:Saturationfield4_3DCases}b,e  and Figs.~\ref{fig:Saturationfield4_3DCases}c,f, it indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern. A detailed quantitative analysis of this upscaled model will be presented in future work.
